Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-09-17 article/manuscript.Rnw
format manuscript for new submission

@@

\author{
\name{L.K.Oshita\textsuperscript{a}\thanks{CONTACT L.K.Oshita. Email: l.oshita@yahoo.com}, A.Pileggi\textsuperscript{b}}
\affil{\textsuperscript{a}iFixit; )
}

@@

% \author[cp]{L.K.~Oshita\corref{cor1}}
% \cortext[cor1]{Corresponding author}
% \ead{l.oshita@yahoo.com}

% \author[ifixit]{A.~Pileggi}
% \author[cp]{S.~Pileggi}

% \address[cp]{Department of Statistics, California Polytechnic State University, San Luis Obispo, CA 93407, United States}
% \address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}

\begin{abstract} 
iFixit's community driven online question and answer forum (CQA), \textif{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair. This platform allows users to ask questions regarding repairs, and for both repair experts and everyday users to provide answers and feedback. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{r2}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = \Sexpr{appleHR}, 95\% CI = (\Sexpr{appleLower}, \Sexpr{appleUpper})), factors related to the question's title (e.g., if it was phrased as a question (HR = \Sexpr{titleHR}, 95\% CI = (\Sexpr{titleLower}, \Sexpr{titleUpper}))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = \Sexpr{dayHR}, 95\% CI = (\Sexpr{dayLower}, \Sexpr{dayUpper}))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract}

\begin{keywords}
Cox regression \sep CQA forum \sep response time \sep survival analysis \sep survival probabilty 
\end{keywords}

@@

Community-driven online question and answer forums feature thousands of user-posted questions and answers and receive millions of visits every month. As such, they have become widely-used sources of information. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit equips users with the knowledge and tools necessary to both repair their broken devices and reduce electronic waste, by providing over 35,000 free online repair guides.

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users. This platform features questions pertaining to over 10,000 devices, ranging from jammed zippers to shattered phone screens and faulty air conditioners, with over 120,000 user-posted solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \citep{Rechavi2011}. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \citet{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \citet{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \citet{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality. \citet{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \citet{Blumenstock2008} also determined that textual features (e.g. word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \citet{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \citep{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.

@@

% Table of derived predictors
\begin{table}%[!htbp]
\tbl{Categorical and continuous variables derived}
% \centering
{\begin{tabular}{|L{2cm}|L{10cm}|}
  \hline
  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
  & If the question's text is in all lower case \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
  & If the question's title ends in a question mark \\ \cline{2-2}
  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & If the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
\end{tabular}}
% \caption{Categorical and continuous variables derived}
\label{table:1}
\end{table}

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \citep{Kleinbaum2011}.

Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \citep{Bland1998}. From these estimates, survival curves were constructed to examine the survival experience of questions. Mean and median survival times were also generated.

As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \citep{Moore2010}. To build the model, five-fold cross-validation was used \citep{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \citep{Hammermeister1979}. Each predictor was entered into univariate Cox models and the evidence of association with response times was assessed. Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.  Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \citep{Harrell2015}. All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \citet{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.

In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \citep{Chen}. Significant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $\chi^2$ distribution \citep{Oakes1981}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \citep{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \citep{Grambsch1994}. Significant correlations would indicate a predictor has violated this assumption.

@@

\section{Results and Discussion}

@@

% Cross-validation metrics
\begin{table}[!htbp]
% \centering
\tbl{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)}
{\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}}
\label{table:3}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
% \centering
\tbl{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
{\begin{tabular}{|l L{5.5cm}|c|c|}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
                  & Camera & -0.32 (0.090) & \\ 
                  & Electronics & -0.01 (0.078)  & \\ 
                  & Game Console & 0.24 (0.083)  & \\ 
                  & Home & 0.34 (0.070) &  \\ 
                  & Other & -0.13 (0.056)  & \\ 
                  & PC & 0.28 (0.060) &  \\ 
                  & Tablet & -0.16 (0.081)  & \\ 
                  & Vehicle & 0.40 (0.069)  & \\
                  & Android/Other Phone (reference) & --- & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
\end{tabular}}
\label{table:4}
\end{table}

@@

\section{Conclusion}

@@

\section{Vitae}

Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo. Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo. Anthony Pileggi is a Data Scientist at iFixit. Declarations of interest: none.

\section{Author Contributions}

All authors contributed to the analysis featured in this paper and have edited and approved of the final article.

\section{Acknowledgements}

This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. This sponsor was not involved in any aspect of this paper's analysis. We also thank iFixit for providing access to the CQA data.

\section{Appendix}

\subsection{Posted questions}

\begin{table}[!htbp]
% \centering
\tbl{Examples of an answered question (left) and an unanswered question (right)}
{\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
\hline
\textbf{Device} & iPhone 6 & android tablet \\ \hline
\textbf{Title} & iPhone water damage, touch screen issue & ccccaaaan you help me fix my touch screen \\ \hline
\textbf{Text} & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & touch screen not worki\\ \hline
\textbf{Tags} & touchscreen, water damage & NA\\ \hline
\textbf{Response Time (hrs)} & 1.361 & NA \\ \hline 
\textbf{Device Category} & Apple Product & Tablet \\ \hline
\textbf{Day Posted} & Weekday & Weekday \\ \hline
\textbf{Text length (characters)} & 241 & 81 \\ \hline
\textbf{Device name length (characters)} & 8 & 18\\ \hline
\textbf{Average tag length (characters)} & 11.5 & 47 \\ \hline
\textbf{Average tag frequency} & 0.0097 & 0 \\ \hline
\textbf{Text contain end punctuation?} & True & False \\ \hline
\textbf{Text in all lower case?} & False & True \\ \hline
\textbf{Title end in a question mark?} & False & False \\ \hline
\textbf{Line break to text length ratio} & 0 & 0 \\ \hline
\textbf{User indicate prior effort?} & False & False \\ \hline
\textbf{User update question after posting?} & False & False \\ \hline
\textbf{Frequently-used answered words?} & True & True \\ \hline
\textbf{Frequently-used unanswered words?} & False & False \\ \hline
\end{tabular}}
\label{table:5}
\end{table}

@@

\subsection{Variable Derivation}

\subsubsection{Average tag frequency}

This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times. This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set. Questions without tags were assigned a value of 0.  If a question has a higher average, then at least one of its tags are considered frequently-used. This variable was created based off of findings from \citet{Bhat2014}.

\subsubsection{Average tag length}

@@

\subsubsection{Device categorization}

@@

\subsubsection{Device name length}

@@

\subsubsection{If the question's text contains end punctuation}

@@

\subsubsection{If the question's title contains terms considered frequently-used among answered/unanswered questions}

These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not. Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not. This variable was created based off of methods from \citet{Correa2013} and \citet{Ravi2014}.

@@

@@

\subsubsection{If the question's title ends in a question mark}

This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \citep{Bhat2014}.

\subsubsection{If the user made an effort to solve the problem prior to asking the question}

This variable indicates true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting. Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted. This variable was created based off of findings and methods from \citet{Bhat2014} and \citet{Harper2008}.

\subsubsection{Line break to text length ratio}

\section*{References}

\bibliographystyle{elsarticle-num-names}
\bibliography{references}

>>>>

\usepackage[numbers,sort&compress]{natbib} % for reference/citation formating
\bibpunct[, ]{[}{]}{,}{n}{,}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}

@@

\author{
\name{Lisa Oshita\textsuperscript{a}\thanks{CONTACT Lisa Oshita Email: l.oshita@yahoo.com}, Anthony Pileggi\textsuperscript{b}, Shannon Pileggi\textsuperscript{a}}
\affil{\textsuperscript{a}Department of Statistics, California Polytechnic State University, CA, 93407; \textsuperscript{b}iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}
}

@@

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, contains an extensive amount of crowd-sourced information related specifically to device repair. This platform allows users to ask questions regarding repairs, and for both repair experts and everyday users to provide answers and feedback. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{r2}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = \Sexpr{appleHR}, 95\% CI = (\Sexpr{appleLower}, \Sexpr{appleUpper})), factors related to the question's title (e.g., if it was phrased as a question (HR = \Sexpr{titleHR}, 95\% CI = (\Sexpr{titleLower}, \Sexpr{titleUpper}))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = \Sexpr{dayHR}, 95\% CI = (\Sexpr{dayLower}, \Sexpr{dayUpper}))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract}

\begin{keywords}
Cox regression; CQA forum; response time; survival analysis; survival probabilty 
\end{keywords}

@@

Community-driven online question and answer forums feature thousands of user-generated questions and answers and receive millions of visits every month. As such, they have become widely-used sources of information. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit equips users with the knowledge and tools necessary to both repair their broken devices and reduce electronic waste, by providing over 35,000 free online repair guides.

As not all possible repairs are covered in the published guides and users may have additional questions, iFixit's \textit{Answers} forum is an important resource for users. This platform features questions pertaining to over 10,000 devices, ranging from zippers to air conditioners and phone screens, with over 120,000 user-posted solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times have been shown to be associated with positive user satisfaction and, in turn, increase web traffic, which is valuable to the reputation and longevity of the CQA \cite{Rechavi2011}. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how the forum design can be improved.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock2008} also determined that textual features (e.g. word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{Fu2015} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.

@@

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.

Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}. From these estimates, survival curves were constructed to examine the survival experience of questions. Mean and median survival times were also generated.

As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univariate Cox models and the evidence of association with response times was assessed. Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.  Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \cite{Harrell2015}. All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.

In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Significant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}. Significant correlations would indicate a predictor has violated this assumption.

@@

\section{Results}

@@

@@

@@

\section{Discussion}

@@

% \section{Vitae}
% 
% Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo. Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo. Anthony Pileggi is a Data Scientist at iFixit. Declarations of interest: none.

% \section{Author Contributions}
% 
% All authors contributed to the analysis featured in this paper and have edited and approved of the final article.

\section*{Acknowledgements}

 We would like to thank iFixit for providing access to the CQA data.

\section*{Disclosure Statement}

We wish to confirm that there are no known conflicts of interest associated with this publication.

\section*{Funding}

This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. This sponsor was not involved in any aspect of this paper's analysis.

\bibliographystyle{tfs}
\bibliography{references}

\section{Appendices}

\appendix

\section{Posted questions}

@@

\section{Variable Derivation}

\subsection{Average tag frequency}

This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times. This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set. Questions without tags were assigned a value of 0.  If a question has a higher average, then at least one of its tags are considered frequently-used. This variable was created based off of findings from \cite{Bhat2014}.

\subsection{Average tag length}

@@

\subsection{Device categorization}

@@

\subsection{Device name length}

@@

\subsection{If the question's text contains end punctuation}

@@

\subsection{If the question's title contains terms considered frequently-used among answered/unanswered questions}

These variables were created to investigate if questions pertaining to popular topics receive answers faster than questions that do not. Similarly, another variable was created to investigate if questions pertaining to unpopular topics receive answers slower than questions that do not. This variable was created based off of methods from \cite{Correa2013} and \cite{Ravi2014}.

@@

\subsection{If the question's title ends in a question mark}

This variable was created to investigate if questions with titles in the form of questions receive answers faster than those otherwise phrased \cite{Bhat2014}.

\subsection{If the user made an effort to solve the problem prior to asking the question}

This variable indicates true if the asker included words in the question's text that indicate that prior effort was made to find the solution to the question before posting. Words searched for include: tried, searched, researched, tested, replaced, used, checked, investigated, considered, measured, attempted, inspected, fitted. This variable was created based off of findings and methods from \cite{Bhat2014} and \cite{Harper2008}.

\subsection{Line break to text length ratio}

\end{appendix}

% Table of derived predictors
\begin{table}[p]%[!htbp]
\tbl{Categorical and continuous variables derived}
% \centering
{\begin{tabular}{|L{2cm}|L{10cm}|}
  \hline
  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
  & If the question's text is in all lower case \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
  & If the question's title ends in a question mark \\ \cline{2-2}
  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & If the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
\end{tabular}}
% \caption{Categorical and continuous variables derived}
\label{table:1}
\end{table}

% Cross-validation metrics
\begin{table}%[!htbp]
% \centering
\tbl{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)}
{\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}}
\label{table:3}
\end{table}

% Final model on full data
\begin{table}%[!htbp]
% \centering
\tbl{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
{\begin{tabular}{|l L{5.5cm}|c|c|}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
                  & Camera & -0.32 (0.090) & \\ 
                  & Electronics & -0.01 (0.078)  & \\ 
                  & Game Console & 0.24 (0.083)  & \\ 
                  & Home & 0.34 (0.070) &  \\ 
                  & Other & -0.13 (0.056)  & \\ 
                  & PC & 0.28 (0.060) &  \\ 
                  & Tablet & -0.16 (0.081)  & \\ 
                  & Vehicle & 0.40 (0.069)  & \\
                  & Android/Other Phone (reference) & --- & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
\end{tabular}}
\label{table:4}
\end{table}

\begin{table}%[!htbp]
% \centering
\tbl{Examples of an answered question (left) and an unanswered question (right)}
{\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
\hline
\textbf{Device} & iPhone 6 & android tablet \\ \hline
\textbf{Title} & iPhone water damage, touch screen issue & ccccaaaan you help me fix my touch screen \\ \hline
\textbf{Text} & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & touch screen not worki\\ \hline
\textbf{Tags} & touchscreen, water damage & NA\\ \hline
\textbf{Response Time (hrs)} & 1.361 & NA \\ \hline 
\textbf{Device Category} & Apple Product & Tablet \\ \hline
\textbf{Day Posted} & Weekday & Weekday \\ \hline
\textbf{Text length (characters)} & 241 & 81 \\ \hline
\textbf{Device name length (characters)} & 8 & 18\\ \hline
\textbf{Average tag length (characters)} & 11.5 & 47 \\ \hline
\textbf{Average tag frequency} & 0.0097 & 0 \\ \hline
\textbf{Text contain end punctuation?} & True & False \\ \hline
\textbf{Text in all lower case?} & False & True \\ \hline
\textbf{Title end in a question mark?} & False & False \\ \hline
\textbf{Line break to text length ratio} & 0 & 0 \\ \hline
\textbf{User indicate prior effort?} & False & False \\ \hline
\textbf{User update question after posting?} & False & False \\ \hline
\textbf{Frequently-used answered words?} & True & True \\ \hline
\textbf{Frequently-used unanswered words?} & False & False \\ \hline
\end{tabular}}
\label{table:5}
\end{table}

@@
